\section{Talks}
Henne, P. \& \textbf{O'Neill, K.} Double Prevention, Causal Judgments,
and Counterfactuals. \emph{Invited talk for the Causality in Cognition
Lab, Stanford}.

\textbf{O'Neill, K.}, Henne, P., Pearson, J., De Brigard,
F. (2022). ``Measuring and modeling confidence in human causal
judgment''. \emph{Cognitive Science Society, Society for Philosophy
and Psychology, Southern Society for Philosophy and Psychology}.

Krasich, K., \textbf{O'Neill, K.}, De Brigard, F. (2022). ``Eye
tracking mental simulations during retrospective causal
reasoning''. \emph{Cognitive Science Society, Society for Philosophy
and Psychology, Southern Society for Philosophy and Psychology}.

\textbf{O'Neill, K.} (2022). ``Disentangling Confidence and Causal
Judgment''. \emph{Invited talk for the Consciousness Club, Meta Lab,
University College London}.

\textbf{O'Neill, K.} (2022). ``Confidence \& Singular Causal
Judgment''. \emph{Invited talk for the Cognitive and Neural
Computation Lab, University of California Irvine}.

Khoudary, A., \textbf{O’Neill, K.}, Faul, L., Murray, S., Smallman,
R., De Brigard, F. (2021-2022). Neural differences between internal
and external episodic counterfactual thoughts. \emph{Neuromatch
Conference 4.0}.

\textbf{O'Neill, K.}, Henne, P., Bello, P., Pearson, J., De Brigard,
F. (2021). ``Degrading causation''. \emph{Invited talk at Causal
Cognition Lab, UCL, XPhi Europe}.

Bello, P., \textbf{O'Neill, K.}, Bridewell, W. (2019). ``Artificial
agency requires attention: the case of intentional action''. In
\emph{AAAI Spring Symposium: Towards Conscious AI Systems}.

\textbf{O'Neill, K.}, Bridewell, W., Bello, P. (2018) ``Time-based
resource sharing in ARCADIA''. \emph{40th Annual Meeting of the
Cognitive Science Society}.

\textbf{O’Neill, K.}, Bringsjord, S. ``Solving the lottery paradox in
a cognitive calculus''. (2016) \emph{International Association for
Computing and Philosophy}.

\line\section{Poster Presentations}

\textbf{O'Neill, K.}, Quillien, T., Henne, P. (2022). ``A
Counterfactual Model of Causal Judgments in Double
Prevention''. \emph{Conference on Cognitive Computational
Neuroscience}.

\textbf{O'Neill, K.}, Krasich, K., Murray, S., Brockmole, J.,
Nuthmann, A., De~Brigard, F. (2022). ``Fixation duration variability
increases with mind wandering during scene viewing''. \emph{Conference
on Cognitive Computational Neuroscience}.

Khoudary, A., \textbf{O’Neill, K.}, Faul, L., Murray, S., Smallman,
R., De Brigard, F. (2022). Neural differences between internal and
external episodic counterfactual thoughts. \emph{Cognitive
Neuroscience Society Annual Meeting}.

\textbf{O'Neill, K.}, Henne, P., Bello, P., Pearson, J., De Brigard,
F. (2021). ``Measuring and modeling confidence in human causal
judgment``. \emph{Workshop on Metacognition in the Age of AI:
Challenges and Opportunities, 35th Conference on Neural Information
Processing Systems (NeurIPS 2021), Sydney, Australia}.

\textbf{O'Neill, K.}, Henne, P., Bello, P., Pearson, J., De Brigard,
F. (2021). ``Confidence effects on causal
judgment``. \emph{Psychonomics}.

\textbf{O'Neill, K.}, Henne, P., Bello, P., Pearson, J., De Brigard,
F. (2021). ``Degrading causation``. \emph{Society for Philosophy and
Psychology Annual Meeting}.

Khoudary, A., Hanna, E., \textbf{O’Neill, K.}, Iyengar, V., Clifford,
S., Cabeza, R., De Brigard, F., Sinnott-Armstrong, W. (2021). ``A
functional neuroimaging investigation of moral foundations
theory''. \emph{Society for Philosophy and Psychology Annual
Meeting}. \emph{2020 meeting of the Cognitive Neuroscience Society}.

Smith, A., \textbf{O'Neill, K.}, Smilek, D., Seli, P. (2019) ``On the
utility of the dynamic framework of mind
wandering''. \emph{Psychonomics}.

Yin, S., \textbf{O'Neill, K.}, Brady, T., De Brigard, F. (2019) ``The
effect of category learning on recognition memory: a signal detection
theory analysis''. \emph{41st Annual Meeting of the Cognitive Science
Society}.

Lovett, A., Briggs, G., \textbf{O'Neill, K.}, Bello,
P. (2018). ``Strategic deployment of attention in online causal
judgment: a computational model''. \emph{Journal of Vision}, 18(10),
741-741.

Bello, P., Lovett, A., Briggs, G., \textbf{O'Neill, K.} (2018) ``An
attention-driven model of human causal reasoning''. \emph{40th Annual
Meeting of the Cognitive Science Society}.
